Open archaeology, open source?

### 2023-10-11 analysis/_04-open_archaeology.qmd
Fix stray chunk boundary

- What kind of projects comprise open archaeology?
  x Breakdown of tags and categories
  x Breakdown of platforms and languages
  x Tags by category
  x Licenses?
- How has this changed over time?
  - Growth of open archaeology by number of commits
  - Growth of open archaeology by number of repos
  - Compare changing proportions of each category on a year by year basis
  - Identify periods associated with different rates of growth, and relate these with different general attitudes in the history of digital archaeology
-->
```

>>>>

- What kind of projects comprise open archaeology?
  x Breakdown of tags and categories
  x Breakdown of platforms and languages
  x Tags by category
  x Licenses?
- How has this changed over time?
  - Growth of open archaeology by number of commits
  - Growth of open archaeology by number of repos
  - Compare changing proportions of each category on a year by year basis
  - Identify periods associated with different rates of growth, and relate these with different general attitudes in the history of digital archaeology
-->
